### 2016-07-02 docs/online_supporting_information.tex
final edits for ELE resubmission
R1 to ELE version

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.0033 & -0.0171 \\ 
  BORO & -0.0050 & -0.0772 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.0300 & 0.0129 & 0.0117 & 0.0003 \\ 
  HECO & -0.0000 & -0.0285 & 0.0084 & -0.0028 \\ 
  POSE & 0.0001 & 0.0032 & -0.0845 & -0.0043 \\ 
  PSSP & -0.0003 & -0.0027 & -0.0004 & -0.0448 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -0.0017 & 0.0011 & 0.0010 \\ 
  BOHI & 0.0002 & -0.0046 & -0.0078 \\ 
  SCSC & -0.0003 & 0.0007 & -0.0124 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.0121 & -0.0002 & -0.0229 & -0.0014 \\ 
  HECO & -0.0023 & -0.0778 & 0.0142 & 0.0061 \\ 
  PASM & -0.0005 & -0.0039 & -0.0601 & -0.0033 \\ 
  POSE & 0.0005 & -0.0101 & -0.0404 & -0.1431 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.0045 & -0.0013 \\ 
  SPFL & -0.0041 & -0.0176 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.2791 & -0.0816 \\ 
  BORO & -0.0200 & -0.6101 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.0236 & -0.0202 & 0.0314 & 0.0158 \\ 
  HECO & -0.0005 & -1.0206 & -0.0052 & 0.0125 \\ 
  POSE & 0.0001 & 0.0006 & -0.9091 & 0.0121 \\ 
  PSSP & 0.0009 & -0.0013 & 0.0246 & -0.1543 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -0.1087 & 0.0006 & 0.0010 \\ 
  BOHI & 0.0021 & -0.0403 & -0.0153 \\ 
  SCSC & -0.0064 & -0.0066 & -0.0270 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.1280 & 0.0211 & 0.1243 & 0.0173 \\ 
  HECO & -0.0043 & -0.5661 & 0.1386 & 0.0013 \\ 
  PASM & 0.0001 & -0.0044 & -1.3046 & 0.0012 \\ 
  POSE & 0.0010 & 0.0085 & 0.1198 & -1.2434 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.1575 & -0.0040 \\ 
  SPFL & -0.0120 & -0.2807 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.5304 & -0.3063 \\ 
  BORO & -0.5798 & -2.3237 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.4054 & 0.2132 & 0.0120 & 0.2389 \\ 
  HECO & -0.5674 & -1.7722 & -0.1476 & -0.3184 \\ 
  POSE & -0.2499 & -0.0328 & -2.2873 & -0.1448 \\ 
  PSSP & -0.2580 & -0.1687 & 0.0365 & -1.7675 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -1.1584 & -0.0242 & -0.0524 \\ 
  BOHI & 0.3387 & -0.8620 & 0.0123 \\ 
  SCSC & 0.0615 & -0.0308 & -0.9543 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.8916 & -0.2522 & -0.1334 & 0.0610 \\ 
  HECO & 0.0852 & -1.4191 & -0.0685 & -0.0422 \\ 
  PASM & 0.1252 & 0.3093 & -4.1823 & 0.3032 \\ 
  POSE & 0.1577 & 0.4906 & 0.0709 & -1.7065 \\ 
   \hline
\end{tabular}
\end{table}\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.7631 & -0.6198 \\ 
  SPFL & -0.0684 & -2.5220 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\subsubsection{Interaction Coefficients for Vital Rates in Arizona}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.0033 & -0.0171 \\ 
  BORO & -0.0050 & -0.0772 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.2791 & -0.0814 \\ 
  BORO & -0.0200 & -0.6102 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Arizona.} 
\begin{tabular}{rrr}
  \hline
 & BOER & BORO \\ 
  \hline
BOER & -0.5184 & -0.3290 \\ 
  BORO & -0.5779 & -2.3235 \\ 
   \hline
\end{tabular}
\end{table}

\subsubsection{Interaction Coefficients for Vital Rates in Idaho}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.0300 & 0.0129 & 0.0117 & 0.0003 \\ 
  HECO & -0.0000 & -0.0285 & 0.0084 & -0.0028 \\ 
  POSE & 0.0001 & 0.0032 & -0.0845 & -0.0043 \\ 
  PSSP & -0.0003 & -0.0027 & -0.0004 & -0.0448 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.0236 & -0.0199 & 0.0314 & 0.0158 \\ 
  HECO & -0.0005 & -1.0206 & -0.0051 & 0.0125 \\ 
  POSE & 0.0001 & 0.0006 & -0.9088 & 0.0121 \\ 
  PSSP & 0.0009 & -0.0013 & 0.0248 & -0.1547 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Idaho.} 
\begin{tabular}{rrrrr}
  \hline
 & ARTR & HECO & POSE & PSSP \\ 
  \hline
ARTR & -0.4003 & 0.2243 & 0.0117 & 0.2360 \\ 
  HECO & -0.5681 & -1.7594 & -0.1437 & -0.3195 \\ 
  POSE & -0.2505 & -0.0131 & -2.2928 & -0.1420 \\ 
  PSSP & -0.2405 & -0.1389 & 0.0347 & -1.7751 \\ 
   \hline
\end{tabular}
\end{table}

\subsubsection{Interaction Coefficients for Vital Rates in Kansas}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -0.0017 & 0.0011 & 0.0010 \\ 
  BOHI & 0.0002 & -0.0046 & -0.0078 \\ 
  SCSC & -0.0003 & 0.0007 & -0.0124 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -0.1084 & 0.0006 & 0.0010 \\ 
  BOHI & 0.0021 & -0.0403 & -0.0153 \\ 
  SCSC & -0.0064 & -0.0066 & -0.0271 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Kansas.} 
\begin{tabular}{rrrr}
  \hline
 & BOCU & BOHI & SCSC \\ 
  \hline
BOCU & -1.1544 & -0.0312 & -0.0643 \\ 
  BOHI & 0.3410 & -0.8681 & 0.0041 \\ 
  SCSC & 0.0619 & -0.0336 & -0.9611 \\ 
   \hline
\end{tabular}
\end{table}

\subsubsection{Interaction Coefficients for Vital Rates in Montana}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.0124 & -0.0032 & -0.0258 & -0.0001 \\ 
  HECO & -0.0025 & -0.0976 & 0.0096 & 0.0079 \\ 
  PASM & -0.0006 & -0.0041 & -0.0695 & -0.0030 \\ 
  POSE & 0.0006 & -0.0082 & -0.0417 & -0.1410 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.1316 & 0.0076 & 0.1096 & 0.0126 \\ 
  HECO & -0.0028 & -0.7064 & 0.1423 & -0.0030 \\ 
  PASM & -0.0012 & -0.0033 & -1.4026 & 0.0024 \\ 
  POSE & 0.0014 & 0.0082 & 0.1363 & -1.2203 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in Montana.} 
\begin{tabular}{rrrrr}
  \hline
 & BOGR & HECO & PASM & POSE \\ 
  \hline
BOGR & -0.9151 & -0.3076 & -0.0984 & 0.0495 \\ 
  HECO & -0.0785 & -1.4192 & -0.0480 & -0.0468 \\ 
  PASM & -0.0103 & 0.2773 & -4.3148 & 0.3470 \\ 
  POSE & 0.1971 & 0.4854 & 0.0623 & -1.7109 \\ 
   \hline
\end{tabular}
\end{table}

\subsubsection{Interaction Coefficients for Vital Rates in New Mexico}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for growth regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.0045 & -0.0013 \\ 
  SPFL & -0.0041 & -0.0176 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for survival regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.1576 & -0.0040 \\ 
  SPFL & -0.0120 & -0.2806 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Interaction coefficients for recruitment regressions in NewMexico.} 
\begin{tabular}{rrr}
  \hline
 & BOER & SPFL \\ 
  \hline
BOER & -0.7649 & -0.6230 \\ 
  SPFL & -0.0691 & -2.5296 \\ 
   \hline
\end{tabular}
\end{table}
